### 2018-05-24 paper.tex
...

@@

\begin{lem} \label{lem:consistency1}
Suppose the conditions of {\color{red} Section} all hold.
Suppose the sample size satisfies
\begin{equation}
n_y
\geq \max\left\{ (C_{n_y} s \log p) \log^3 ( C_{n_y} s \log p ), \frac{32 \kappa_2}{\kappa_1} s_1 \log p \right\}.
\end{equation}
Then, the sparse KLIEP with the regularization parameter
\begin{equation}
\lambda_1 \geq C_1 \sqrt{\log p / n}
\end{equation}
has an optimal solution $\check\fattheta$ satisfying
\begin{equation}
\|\check\fattheta - \fattheta^*\|_1 \leq K_1 \sqrt{s_1^2 \log p / n}
\end{equation}
for some $K_1 > 0$ with probability at least
\begin{equation}
1 - 6\exp(-n \lambda_1^2 / C_1^2).
\end{equation}
\end{lem}

\noindent
$C_1 > 0$ is defined in Lemma \ref{lem:grad1} in Appendix \ref{app:grads}.

\begin{proof}
Define a function $f : \RR^p \to \RR$,
\begin{equation}
f(\fatdelta)
:= \ell_\text{KLIEP}(\fattheta^* + \fatdelta) - \ell_\text{KLIEP}(\fattheta^*) + \lambda_1 \{\|\fattheta^* + \fatdelta\|_1 - \|\fattheta^*\|_1\},
\end{equation}
i.e.~the deviation of the objective from the value at $\fattheta^*$.
We remark that $f(\mathbf{0}) = 0$, and hence $f(\check\fattheta - \fattheta^*) \leq 0$, as $\check\fattheta$ is the minimizer of the objective.
Recall
\begin{equation}
\mathcal{E}_1
= \mathcal{E}(S_1,\fattheta^*)
= \{\fatdelta \in \RR^p : \|\fatdelta_{S_1^c}\|_1 \leq 3\|\fatdelta_{S_1}\|_1\}.
\end{equation}
Put $\check\fatdelta = \check\fattheta - \fattheta^*$.
Our first step is to deduce $\check\fatdelta \in \mathcal{E}_1$ using $f(\check\fatdelta) \leq 0$.
Since $\ell_\text{KLIEP}$ is convex,
\begin{equation}
\ell_\text{KLIEP}(\fattheta^* + \fatdelta) - \ell_\text{KLIEP}(\fattheta^*)
\geq \langle \nabla \ell_\text{KLIEP}(\fattheta^*), \fatdelta \rangle
\geq -\|\nabla \ell_\text{KLIEP}(\fattheta^*)\|_\infty \|\fatdelta\|_1,
\end{equation}
by Cauchy-Schwarz.
On the other hand,
\begin{equation}
\begin{aligned}
\|\fattheta^* + \fatdelta\|_1 - \|\fattheta^*\|_1
&\geq \|\fattheta_{S_1}^* + \fatdelta_{S_1^c}\|_1 - \|\fattheta_{S_1^c}^* + \fatdelta_{S_1}\|_1 - \|\fattheta_{S_1}^* + \fattheta_{S_1^c}^*\|_1 \\
&= \|\fattheta_{S_1}^*\|_1 + \|\fatdelta_{S_1^c}\|_1 - \|\fattheta_{S_1^c}^*\|_1 - \|\fatdelta_{S_1}\|_1 - \|\fattheta_{S_1}^*\|_1 - \|\fattheta_{S_1^c}^*\|_1 \\
&= \|\fatdelta_{S_1^c}\|_1 - \|\fatdelta_{S_1}\|_1 - 2\|\fattheta_{S_1^c}^*\|_1,
\end{aligned}
\end{equation}
and as $\fattheta_{S_1^c}^* = \mathbf{0}$, the inequality simplifies to
\begin{equation}
\|\fattheta^* + \fatdelta\|_1 - \|\fattheta^*\|_1
\geq \|\fatdelta_{S_1^c}\|_1 - \|\fatdelta_{S_1}\|_1.
\end{equation}
Thus,
\begin{equation}
\begin{aligned}
0
\geq f(\check\fatdelta)
&= \ell_\text{KLIEP}(\fattheta^* + \check\fatdelta) - \ell_\text{KLIEP}(\fattheta^*) + \lambda_1 \{\|\fattheta^* + \check\fatdelta\|_1 - \|\fattheta^*\|_1\} \\
&\geq -\|\nabla \ell_\text{KLIEP}(\fattheta^*)\|_\infty \|\fatdelta\|_1 + \lambda_1 \{\|\fatdelta_{S_1^c}\|_1 - \|\fatdelta_{S_1}\|_1\}.
\end{aligned}
\end{equation}
By Lemma \ref{lem:grad1},
\begin{equation} \label{eq:applying_grad1}
\PP\left\{ \|\nabla \ell_\text{KLIEP}(\fattheta^*)\|_\infty \leq \lambda_1 / 2 \right\}
\geq 1 - 6\exp(-n \lambda_1^2 / C_1^2).
\end{equation}
Thus,
\begin{equation}
0 \geq -\frac{\lambda_1}{2} \|\fatdelta\|_1 + \lambda_1 \{\|\fatdelta_{S_1^c}\|_1 - \|\fatdelta_{S_1}\|_1\}.
\end{equation}
Since $\lambda_1 > 0$, we must have $\check\fatdelta \in \mathcal{E}_1$.

@@

For the last step, fix $0 < \rho < \diam(\mathcal{U}(\fattheta))$, and suppose $\fatdelta \in \mathcal{E}_1$ with $\|\fatdelta\| = \rho$.
By Taylor's theorem,
\begin{equation}
\ell_\text{KLIEP}(\fattheta^*+\fatdelta) - \ell_\text{KLIEP}(\fattheta^*)
= \langle \nabla \ell_\text{KLIEP}(\fattheta^*), \fatdelta \rangle + \frac{1}{2} \fatdelta^\top \bar\Hb \fatdelta,
\end{equation}
where
\begin{equation}
\bar\Hb = \int_0^1 \nabla^2 \ell_\text{KLIEP}(\fattheta^*+t\fatdelta) \, dt.
\end{equation}
By Proposition \ref{prop:RSC},
\begin{equation}
\fatdelta^\top \bar\Hb \fatdelta
\geq \kappa \|\fatdelta\|^2 - \kappa_3 \frac{\log p}{n_y} \|\fatdelta\|_1^2
\geq \left( \kappa - 16 \kappa_3 \frac{s_1 \log p}{n_y} \right) \|\fatdelta\|^2
\geq \frac{\kappa}{2}  \|\fatdelta\|^2,
\end{equation}
where the last inequality uses $n_y \geq 32 (\kappa_3 / \kappa) s_1 \log p$.
Thus,
\begin{equation}
\begin{aligned}
f(\fatdelta)
&= \ell_\text{KLIEP}(\fattheta^* + \fatdelta) - \ell_\text{KLIEP}(\fattheta^*) + \lambda_1 \{\|\fattheta^* + \fatdelta\|_1 - \|\fattheta^*\|_1\} \\
&= \frac{1}{2} \fatdelta^\top \bar\Hb \fatdelta + \langle \nabla \ell_\text{KLIEP}(\fattheta^*), \fatdelta \rangle + \lambda_1 \{\|\fattheta^* + \fatdelta\|_1 - \|\fattheta^*\|_1\} \\
&\geq \frac{\kappa}{4} \|\fatdelta\|^2 + \langle \nabla \ell_\text{KLIEP}(\fattheta^*), \fatdelta \rangle + \lambda_1 \{\|\fattheta^* + \fatdelta\|_1 - \|\fattheta^*\|_1\}.
\end{aligned}
\end{equation}
On the other hand,
\begin{multline}
\langle \nabla \ell_\text{KLIEP}(\fattheta^*), \fatdelta \rangle + \lambda_1 \{\|\fattheta^* + \fatdelta\|_1 - \|\fattheta^*\|_1\} \\
\geq -\frac{\lambda_1}{2} \{\|\fatdelta_{S_1^c}\| + \|\fatdelta_{S_1}\|_1\} + \lambda_1 \{\|\fatdelta_{S_1^c}\| - \|\fatdelta_{S_1}\|_1\} \\
\geq -\frac{3}{2} \lambda_1 \|\fatdelta_{S_1}\|_1 + \frac{1}{2} \lambda_1 \|\fatdelta_{S_1^c}\|_1
\geq -\frac{3}{2} \lambda_1 \|\fatdelta_{S_1}\|_1
\geq -\frac{3}{2} \lambda_1 \sqrt{s_1	} \|\fatdelta\|.
\end{multline}
Therefore,
\begin{equation}
f(\fatdelta)
\geq \frac{\kappa}{4} \|\fatdelta\|^2 - \frac{3}{2} \lambda_1 \sqrt{s} \|\fatdelta\|.
\end{equation}
This is strictly positive when $\|\fatdelta\| > 6 \lambda_1 \sqrt{s_1} / \kappa$, and hence
\begin{equation}
\|\check\fattheta - \fattheta^*\| \leq \frac{6 C_1}{\kappa} \sqrt{\frac{s_1 \log p}{n}}.
\end{equation}
Finally,
\begin{equation}
\|\check\fattheta - \fattheta^*\|_1
\leq 4 \sqrt{s_1} \|\check\fattheta - \fattheta^*\|
\leq \frac{24 C_1}{\kappa} \sqrt{\frac{s_1^2 \log p}{n}}.
\end{equation}
\end{proof}

\begin{lem} \label{lem:consistency2}
Suppose Assumptions \ref{hyp:BSS}, \ref{hyp:IPC}, \ref{hyp:sp} and \ref{hyp:CRME} all hold.
Assume, in addition, that
\begin{equation}
n \geq (K_1 / \|\fattheta^*\|)^2 s_1^2 \log p
\quad \text{and} \quad
n_y \geq (2 \kappa_2 / \kappa_1) s_2 \log p.
\end{equation}
Then, the solution to the second step optimization problem with regularization parameter $\lambda_2(n) \geq (C_\mu \vee C_\mu' s) \, \|\fatomega_{n_y}^*\|_1 \sqrt{\log p / n}$ has an optimal solution $\check\fatomega$ satisfying
\begin{equation}
\|\check\fatomega - \fatomega_{n_y}^*\|_1 = O_{\PP}\left( \sqrt{\frac{s_2^3 \log p}{n}} \right)
\end{equation}
for some $K_2 > 0$ with probability at least
\end{lem}

@@

Recall that $\fatomega_{n_y}^*$ partitions into strong signals $\fatomega_{n_y,S_2}^*$ and weak signals $\fatomega_{n_y,S_2^c}^*$ with
\begin{equation}
\|\fatomega_{n_y,S_2^c}^*\|_1 \leq C_\omega \frac{\log p}{n_y} \|\fatomega_{n_y,S_2}^*\|_1.
\end{equation}
and that
\begin{equation}
\mathcal{E}_2
= \mathcal{E}(S_2,\fatomega_{n_y}^*)
= \{\fatdelta \in \RR^p : \|\fatdelta_{S_2^c}\|_1 \leq 3\|\fatdelta_{S_2}\|_1 + 4\|\fatomega_{n_y,S_2^c}^*\|_1\}.
\end{equation}

@@

We now come to the final step.
Since $\ell_\text{de-bias}$ is quadratic in $\fatomega$, the second-order Taylor expansion is exact, and we actually have
\begin{equation}
\ell_\text{de-bias}(\fatomega_{n_y}^*+\fatdelta) - \ell_\text{de-bias}(\fatomega_{n_y}^*)
= \langle \nabla \ell_\text{de-bias}(\fatomega_{n_y}^*), \fatdelta \rangle + \frac{1}{2} \fatdelta^\top \nabla^2 \ell_\text{KLIEP}(\check\fattheta) \fatdelta.
\end{equation}
As before, we would like to appeal to Proposition \ref{prop:RSC} to bound the quadratic term from the below.
Looking at the conditions of Proposition \ref{prop:URSC}, we are able to do this, so long as $\check\fattheta \in \mathcal{U}(\fattheta^*)$, and by the previous lemma, this is the case with probability at least $1 - 6\exp(n \lambda_1^2 / C_1^2)$.
\begin{equation}
n \geq (K_1 / \|\fattheta^*\}|)^2 s_1^2 \log p.
\end{equation}

With only an approximately sparsity assumption $\fatomega_{n_y}^*$, the second bound in the conclusion of Proposition \ref{prop:RSC} applies, which is
\begin{multline}
\fatdelta^\top \nabla^2 \ell_\text{KLIEP}(\check\fattheta) \fatv
\geq \left( \kappa_1 - \kappa_2 \frac{s_2 \log p}{n_y} \right) \|\fatdelta\|^2 \\
- \left( \tau_1 \sqrt{\frac{\log p}{n_y}} + \tau_2 s_2 \sqrt{\frac{\log p}{n_y}} + \tau_3 s_2 \left( \frac{\log p}{n_y} \right)^{3/2} \right) \|\fatdelta\| - \tau_4 s_2 \left( \frac{\log p}{n_y} \right)^2.
\end{multline}
Also,
\begin{equation}
\begin{aligned}
\langle \nabla \ell_\text{de-bias}(\fatomega_{n_y}^*), \fatdelta \rangle &+ \lambda_2 \{\|\fatomega_{n_y}^* + \fatdelta\|_1 - \|\fatomega_{n_y}^*\|_1\} \\
&\geq -\frac{\lambda_2}{2} \{\|\fatdelta_{S_2^c}\| + \|\fatdelta_{S_2}\|_1\} + \lambda_2 \{\|\fatdelta_{S_2^c}\| - \|\fatdelta_{S_2}\|_1 - 2\|\fatomega_{S_2^c}^*\|_1\} \\
&\geq -\frac{3}{2} \lambda_2 \|\fatdelta_{S_2}\|_1 - 2\lambda_2 \|\fatomega_{S_2^c}^*\|_1 + \frac{1}{2} \lambda_2 \|\fatdelta_{S_2^c}\|_1 \\
&\geq -\frac{3}{2} \lambda_2 \|\fatdelta_{S_2}\|_1 - 2\lambda_2 \|\fatomega_{S_2^c}^*\|_1 \\
&\geq -\frac{3}{2} \lambda_2 \sqrt{s_2} \|\fatdelta\| - \frac{2C_\omega}{\lambda_{\min}} \lambda_2 \sqrt{\frac{s_2 \log p}{n_y}}.
\end{aligned}
\end{equation}
Collecting terms,
\begin{multline} \label{eq:f(delta)}
f(\fatdelta)
\geq \frac{1}{2} \left( \kappa_1 - \kappa_2 \frac{s_2 \log p}{n_y} \right) \|\fatdelta\|^2 \\
- \frac{1}{2} \left( \tau_1 \sqrt{\frac{\log p}{n_y}} + \tau_2 s_2 \sqrt{\frac{\log p}{n_y}} + \tau_3 s_2 \left( \frac{\log p}{n_y} \right)^{3/2} + 3\lambda_2 \sqrt{s_2} \right) \|\fatdelta\| \\
- \frac{\tau_4}{2} s_2 \left( \frac{\log p}{n_y} \right)^2 - \frac{2C_\omega}{\lambda_{\min}} \lambda_2 \sqrt{\frac{s_2 \log p}{n_y}}.
\end{multline}
Provided $n_y \geq 2 (\kappa_2 / \kappa_1) s_2 \log p$,
\begin{equation}
\frac{1}{2} \left( \kappa_1 - \kappa_2 \frac{s_2 \log p}{n_y} \right) \geq \frac{\kappa_1}{4} := a
\end{equation}
is positive.
Plugging in $\lambda_2 = C_2 s_1 \sqrt{s_2 \log p / n} + C_\omega C_2 s_1 \sqrt{s_2} \log p / \sqrt{n n_y}$,
\begin{multline}
\tau_1 \sqrt{\frac{\log p}{n_y}} + \tau_2 s_2 \sqrt{\frac{\log p}{n_y}} + \tau_3 s_2 \left( \frac{\log p}{n_y} \right)^{3/2} + 3\lambda_2 \sqrt{s_2} \\
= \tau_1 \sqrt{\frac{\log p}{n_y}} + \tau_2 s_2 \sqrt{\frac{\log p}{n_y}} + \tau_3 s_2 \left( \frac{\log p}{n_y} \right)^{3/2} + 3C_2 s_1 s_2 \sqrt{\frac{\log p}{n}} + 3 C_\omega C_2 s_1 s_2 \frac{\log p}{n}
\end{multline}
and
\begin{multline}
\frac{\tau_4}{2} s_2 \left( \frac{\log p}{n_y} \right)^2 + \frac{2C_\omega}{\lambda_{\min}} \lambda_2 \sqrt{\frac{s_2 \log p}{n_y}} \\
= \frac{\tau_4}{2} s_2 \left( \frac{\log p}{n_y} \right)^2 + \frac{2C_\omega C_2}{\lambda_{\min}} s_1 s_2 \frac{\log p}{\sqrt{n n_y}} + \frac{2C_\omega^2 C_2}{\lambda_{\min}} s_1 s_2 \frac{\log p}{\sqrt{n n_y}}.
\end{multline}

>>>>

\begin{prop} \label{prop:rsc}
Let $\fattheta \in \mathcal{U}(\fattheta^*)$.
Let
\begin{equation}
\mathcal{E}_1 := \mathcal{E}(S_1;\fattheta^*)
\quad \text{and} \quad
\mathcal{E}_2 := \mathcal{E}(S_2;\fatomega_{n_y}^*).
\end{equation}
Then, with probability at least $1 - \exp(-C_{S_{\psi(y)}} n_y / s) - 2/p$,
\begin{enumerate}
\item for all $\fatv \in \mathcal{E}_1$,
\begin{equation}
\fatv^\top \nabla^2 \ell_\text{KLIEP}(\fattheta) \fatv \geq \left( \kappa_1 - \kappa_2 \frac{s_1 \log p}{n_y} \right) \|\fatv\|^2,
\end{equation}
\item for all $\fatv \in \mathcal{E}_2$,
\begin{multline}
\fatv^\top \nabla^2 \ell_\text{KLIEP}(\fattheta) \fatv
\geq \left( \kappa_1 - \kappa_2 \frac{s_2 \log p}{n_y} \right) \|\fatv\|^2 \\
- \left( \tau_1 \sqrt{\frac{\log p}{n_y}} + \tau_2 s_2 \sqrt{\frac{\log p}{n_y}} + \tau_3 s_2 \left( \frac{\log p}{n_y} \right)^{3/2} \right) \|\fatv\| - \tau_4 s_2 \left( \frac{\log p}{n_y} \right)^2.
\end{multline}
\end{enumerate}
$\kappa_1, \kappa_2, \tau_1, \tau_2, \tau_3, \tau_4 > 0$ are constants defined in the proof.
\end{prop}

@@

Assume the bounded density ratio model.

\begin{lem} \label{lem:consistency1}
Suppose the $\faty$-sample size satisfies
\begin{equation}
n_y \geq \max\{ (C_{n_y} s \log p) \log^3 ( C_{n_y} s \log p ), 2 (\kappa_2 / \kappa_1) s_1 \log p \}.
\end{equation}
Then, the sparse KLIEP with the regularization parameter
\begin{equation}
\lambda_1 \geq C_1 \sqrt{\log p / n}
\end{equation}
has an optimal solution $\check\fattheta$ satisfying
\begin{equation}
\|\check\fattheta - \fattheta^*\|_1 \leq K_1 s_1 \sqrt{\log p / n}
\end{equation}
for some $K_1 > 0$ with probability at least
\begin{equation}
1 - 6\exp(-n \lambda_1^2 / C_1^2).
\end{equation}
\end{lem}

\begin{proof}
Define a function $f : \RR^p \to \RR$,
\begin{equation}
f(\fatdelta)
:= \ell_\text{KLIEP}(\fattheta^* + \fatdelta) - \ell_\text{KLIEP}(\fattheta^*) + \lambda_1 \{\|\fattheta^* + \fatdelta\|_1 - \|\fattheta^*\|_1\},
\end{equation}
i.e.~the deviation of the objective from the value at $\fattheta^*$.
We remark that $f(\mathbf{0}) = 0$, and hence $f(\check\fattheta - \fattheta^*) \leq 0$, as $\check\fattheta$ is the minimizer of the objective.
Recall
\begin{equation}
\mathcal{E}_1
= \mathcal{E}(S_1,\fattheta^*)
= \{\fatdelta \in \RR^p : \|\fatdelta_{S_1^c}\|_1 \leq 3\|\fatdelta_{S_1}\|_1\}.
\end{equation}
Put $\check\fatdelta = \check\fattheta - \fattheta^*$.
Our first step is to deduce $\check\fatdelta \in \mathcal{E}_1$ using $f(\check\fatdelta) \leq 0$.
Since $\ell_\text{KLIEP}$ is convex,
\begin{equation}
\ell_\text{KLIEP}(\fattheta^* + \fatdelta) - \ell_\text{KLIEP}(\fattheta^*)
\geq \langle \nabla \ell_\text{KLIEP}(\fattheta^*), \fatdelta \rangle
\geq -\|\nabla \ell_\text{KLIEP}(\fattheta^*)\|_\infty \|\fatdelta\|_1,
\end{equation}
by Cauchy-Schwarz.
On the other hand,
\begin{equation}
\begin{aligned}
\|\fattheta^* + \fatdelta\|_1 - \|\fattheta^*\|_1
&\geq \|\fattheta_{S_1}^* + \fatdelta_{S_1^c}\|_1 - \|\fattheta_{S_1^c}^* + \fatdelta_{S_1}\|_1 - \|\fattheta_{S_1}^* + \fattheta_{S_1^c}^*\|_1 \\
&= \|\fattheta_{S_1}^*\|_1 + \|\fatdelta_{S_1^c}\|_1 - \|\fattheta_{S_1^c}^*\|_1 - \|\fatdelta_{S_1}\|_1 - \|\fattheta_{S_1}^*\|_1 - \|\fattheta_{S_1^c}^*\|_1 \\
&= \|\fatdelta_{S_1^c}\|_1 - \|\fatdelta_{S_1}\|_1 - 2\|\fattheta_{S_1^c}^*\|_1,
\end{aligned}
\end{equation}
and as $\fattheta_{S_1^c}^* = \mathbf{0}$, the inequality simplifies to
\begin{equation}
\|\fattheta^* + \fatdelta\|_1 - \|\fattheta^*\|_1
\geq \|\fatdelta_{S_1^c}\|_1 - \|\fatdelta_{S_1}\|_1.
\end{equation}
Thus,
\begin{equation}
\begin{aligned}
0
\geq f(\check\fatdelta)
&= \ell_\text{KLIEP}(\fattheta^* + \check\fatdelta) - \ell_\text{KLIEP}(\fattheta^*) + \lambda_1 \{\|\fattheta^* + \check\fatdelta\|_1 - \|\fattheta^*\|_1\} \\
&\geq -\|\nabla \ell_\text{KLIEP}(\fattheta^*)\|_\infty \|\fatdelta\|_1 + \lambda_1 \{\|\fatdelta_{S_1^c}\|_1 - \|\fatdelta_{S_1}\|_1\}.
\end{aligned}
\end{equation}
By Lemma \ref{lem:grad1},
\begin{equation} \label{eq:applying_grad1}
\PP\{ 2\|\nabla \ell_\text{KLIEP}(\fattheta^*)\|_\infty \leq \lambda_1 \}
\geq 1 - 6\exp(-n \lambda_1^2 / C_1^2).
\end{equation}
so that
\begin{equation}
0 \geq -\frac{\lambda_1}{2} \|\fatdelta\|_1 + \lambda_1 \{\|\fatdelta_{S_1^c}\|_1 - \|\fatdelta_{S_1}\|_1\}
\end{equation}
with probability at least $1 - 6\exp(-n \lambda_1^2 / C_1^2)$.
Since $\lambda_1 > 0$, we must have $\check\fatdelta \in \mathcal{E}_1$.

@@

For the last step, fix $0 < \rho < \diam(\mathcal{U}(\fattheta))$, and suppose $\fatdelta \in \mathcal{E}_1$ with $\|\fatdelta\| = \rho$.
By Taylor's theorem,
\begin{equation}
\ell_\text{KLIEP}(\fattheta^*+\fatdelta) - \ell_\text{KLIEP}(\fattheta^*)
= \langle \nabla \ell_\text{KLIEP}(\fattheta^*), \fatdelta \rangle + \frac{1}{2} \fatdelta^\top \bar\Hb \fatdelta,
\end{equation}
where
\begin{equation}
\bar\Hb = \int_0^1 \nabla^2 \ell_\text{KLIEP}(\fattheta^*+t\fatdelta) \, dt.
\end{equation}
By Proposition \ref{prop:rsc} and using the bound on the $\faty$-sample size,
\begin{equation}
\fatdelta^\top \bar\Hb \fatdelta
\geq \left( \kappa_1 - \kappa_2 \frac{s_1 \log p}{n_y} \right) \|\fatdelta\|^2
\geq \frac{\kappa_1}{2}  \|\fatdelta\|^2
\end{equation}
with probability at least $1 - \exp(-C_{S_{\psi(y)}} n_y / s) - 2/p$.
Thus,
\begin{equation}
\begin{aligned}
f(\fatdelta)
&= \ell_\text{KLIEP}(\fattheta^* + \fatdelta) - \ell_\text{KLIEP}(\fattheta^*) + \lambda_1 \{\|\fattheta^* + \fatdelta\|_1 - \|\fattheta^*\|_1\} \\
&= \frac{1}{2} \fatdelta^\top \bar\Hb \fatdelta + \langle \nabla \ell_\text{KLIEP}(\fattheta^*), \fatdelta \rangle + \lambda_1 \{\|\fattheta^* + \fatdelta\|_1 - \|\fattheta^*\|_1\} \\
&\geq \frac{\kappa_1}{4} \|\fatdelta\|^2 + \langle \nabla \ell_\text{KLIEP}(\fattheta^*), \fatdelta \rangle + \lambda_1 \{\|\fattheta^* + \fatdelta\|_1 - \|\fattheta^*\|_1\}
\end{aligned}
\end{equation}
with the same probability.
On the other hand,
\begin{equation}
\begin{aligned}
\langle \nabla \ell_\text{KLIEP}(\fattheta^*), \fatdelta \rangle + \lambda_1 \{\|\fattheta^* + \fatdelta\|_1 - \|\fattheta^*\|_1\}
&\geq -\frac{\lambda_1}{2} \{\|\fatdelta_{S_1^c}\| + \|\fatdelta_{S_1}\|_1\} + \lambda_1 \{\|\fatdelta_{S_1^c}\| - \|\fatdelta_{S_1}\|_1\} \\
&\geq -\frac{3}{2} \lambda_1 \|\fatdelta_{S_1}\|_1 + \frac{1}{2} \lambda_1 \|\fatdelta_{S_1^c}\|_1 \\
&\geq -\frac{3}{2} \lambda_1 \|\fatdelta_{S_1}\|_1 \\
&\geq -\frac{3}{2} \lambda_1 \sqrt{s_1} \|\fatdelta\|
\end{aligned}
\end{equation}
with probability at least $1 - 6\exp(-n \lambda_1^2 / C_1^2)$.
Therefore,
\begin{equation}
f(\fatdelta)
\geq \frac{\kappa_1}{4} \|\fatdelta\|^2 - \frac{3}{2} \lambda_1 \sqrt{s_1} \|\fatdelta\|
\end{equation}
with probability at least $1 - 6\exp(-n \lambda_1^2 / C_1^2) - \exp(-C_{S_{\psi(y)}} n_y / s) - 2/p$.
This is strictly positive for $\|\fatdelta\| > (6 / \kappa_1) \sqrt{s_1} \lambda_1$, and hence
\begin{equation}
\|\check\fattheta - \fattheta^*\| \leq \frac{6 C_1}{\kappa_1} \sqrt{\frac{s_1 \log p}{n}}
\end{equation}
with the same probability
Finally,
\begin{equation}
\|\check\fattheta - \fattheta^*\|_1
\leq 4 \sqrt{s_1} \|\check\fattheta - \fattheta^*\|
\leq \frac{24 C_1}{\kappa_1} s_1 \sqrt{\frac{\log p}{n}}
\end{equation}
with the same probability.
\end{proof}

\begin{lem} \label{lem:consistency2}
Suppose the sample sizes satisfy
\begin{equation}
n \geq (K_1 / \|\fattheta^*\|)^2 s_1^2 \log p
\quad\text{and}\quad
n_y \geq \max\{ (C_{n_y} s \log p) \log^3 ( C_{n_y} s \log p ), 2 (\kappa_2 / \kappa_1) s_1 \log p \}.
\end{equation}
Then, the sparse Hessian inversion problem with the regularization parameter
\begin{equation}
\lambda_2 \geq C_2 \left( 1+C_\omega \sqrt{\log p / n_y} \right) \sqrt{\log p / n}
\end{equation}
has an optimal solution $\check\fatomega$ satisfying
\begin{equation}
\|\check\fatomega - \fatomega_{n_y}^*\|_1 = O_{\PP}\left( s_1s_2^{3/2} \sqrt{\log p / n_y} \right).
\end{equation}
\end{lem}

@@

Recall that $\fatomega_{n_y}^*$ partitions into strong signals $\fatomega_{n_y,S_2}^*$ and weak signals $\fatomega_{n_y,S_2^c}^*$ with
\begin{equation}
\|\fatomega_{n_y,S_2^c}^*\|_1 \leq C_\omega \sqrt{\frac{\log p}{n_y}} \|\fatomega_{n_y,S_2}^*\|_1.
\end{equation}
and that
\begin{equation}
\mathcal{E}_2
= \mathcal{E}(S_2,\fatomega_{n_y}^*)
= \{\fatdelta \in \RR^p : \|\fatdelta_{S_2^c}\|_1 \leq 3\|\fatdelta_{S_2}\|_1 + 4\|\fatomega_{n_y,S_2^c}^*\|_1\}.
\end{equation}

@@

We now come to the final step.
Since $\ell_\text{de-bias}$ is quadratic in $\fatomega$, the second-order Taylor expansion is exact, and we actually have
\begin{equation}
\ell_\text{de-bias}(\fatomega_{n_y}^*+\fatdelta) - \ell_\text{de-bias}(\fatomega_{n_y}^*)
= \langle \nabla \ell_\text{de-bias}(\fatomega_{n_y}^*), \fatdelta \rangle + \frac{1}{2} \fatdelta^\top \nabla^2 \ell_\text{KLIEP}(\check\fattheta) \fatdelta.
\end{equation}
As before, we would like to appeal to Proposition \ref{prop:rsc} to bound the quadratic term from the below.
Proposition \ref{prop:rsc} applies to $\fattheta \in \mathcal{U}(\fattheta^*)$.
By Lemma \ref{lem:consistency1}, it suffices to assume $n \geq (K_1 / \|\fattheta^*\}|)^2 s_1^2 \log p$ to conclude that
$\check\fattheta \in \mathcal{U}(\fattheta^*)$ with probability at least $1 - 6\exp(-n \lambda_1^2 / C_1^2) - \exp(-C_{S_{\psi(y)}} n_y / s) - 2/p$.

With only an approximately sparsity assumption $\fatomega_{n_y}^*$, the second bound of the proposition applies, and this is
\fatdelta^\top \nabla^2 \ell_\text{KLIEP}(\check\fattheta) \fatv
\geq \left( \kappa_1 - \kappa_2 \frac{s_2 \log p}{n_y} \right) \|\fatdelta\|^2 \\
- \left( \tau_1 \sqrt{\frac{\log p}{n_y}} + \tau_2 s_2 \sqrt{\frac{\log p}{n_y}} + \tau_3 s_2 \left( \frac{\log p}{n_y} \right)^{3/2} \right) \|\fatdelta\| - \tau_4 s_2 \left( \frac{\log p}{n_y} \right)^2.
\langle \nabla \ell_\text{de-bias}(\fatomega_{n_y}^*), \fatdelta \rangle &+ \lambda_2 \{\|\fatomega_{n_y}^* + \fatdelta\|_1 - \|\fatomega_{n_y}^*\|_1\} \\
&\geq -\frac{\lambda_2}{2} \{\|\fatdelta_{S_2^c}\| + \|\fatdelta_{S_2}\|_1\} + \lambda_2 \{\|\fatdelta_{S_2^c}\| - \|\fatdelta_{S_2}\|_1 - 2\|\fatomega_{S_2^c}^*\|_1\} \\
&\geq -\frac{3}{2} \lambda_2 \|\fatdelta_{S_2}\|_1 - 2\lambda_2 \|\fatomega_{S_2^c}^*\|_1 + \frac{1}{2} \lambda_2 \|\fatdelta_{S_2^c}\|_1 \\
&\geq -\frac{3}{2} \lambda_2 \|\fatdelta_{S_2}\|_1 - 2\lambda_2 \|\fatomega_{S_2^c}^*\|_1 \\
&\geq -\frac{3}{2} \lambda_2 \sqrt{s_2} \|\fatdelta\| - \frac{2C_\omega}{\lambda_{\min}} \lambda_2 \sqrt{\frac{s_2 \log p}{n_y}}.
Collecting terms,
\begin{multline} \label{eq:f(delta)}
f(\fatdelta)
\geq \frac{1}{2} \left( \kappa_1 - \kappa_2 \frac{s_2 \log p}{n_y} \right) \|\fatdelta\|^2 \\
- \frac{1}{2} \left( \tau_1 \sqrt{\frac{\log p}{n_y}} + \tau_2 s_2 \sqrt{\frac{\log p}{n_y}} + \tau_3 s_2 \left( \frac{\log p}{n_y} \right)^{3/2} + 3\lambda_2 \sqrt{s_2} \right) \|\fatdelta\| \\
- \frac{\tau_4}{2} s_2 \left( \frac{\log p}{n_y} \right)^2 - \frac{2C_\omega}{\lambda_{\min}} \lambda_2 \sqrt{\frac{s_2 \log p}{n_y}}.
Since $n_y \geq 2 (\kappa_2 / \kappa_1) s_2 \log p$,
\frac{1}{2} \left( \kappa_1 - \kappa_2 \frac{s_2 \log p}{n_y} \right) \geq \frac{\kappa_1}{4} := a > 0.
Plugging in $\lambda_2 = C_2 ( 1+C_\omega \sqrt{\log p / n_y} ) s_1 \sqrt{s_2 \log p / n}$,
& \frac{1}{2} \left( \tau_1 \sqrt{\frac{\log p}{n_y}} + \tau_2 s_2 \sqrt{\frac{\log p}{n_y}} + \tau_3 s_2 \left( \frac{\log p}{n_y} \right)^{3/2} + 3\lambda_2 \sqrt{s_2} \right) \\
= & \frac{1}{2} \left( \tau_1 \sqrt{\frac{\log p}{n_y}} + \tau_2 s_2 \sqrt{\frac{\log p}{n_y}} + \tau_3 s_2 \left( \frac{\log p}{n_y} \right)^{3/2} + 3 C_2 \left( 1+C_\omega \sqrt{\frac{\log p}{n_y}} \right) s_1 s_2 \sqrt{\frac{\log p}{n}} \right) \\
\leq & \frac{1}{2} \left( \tau_1 \sqrt{\frac{\log p}{n}} + \tau_2 s_2 \sqrt{\frac{\log p}{n}} + \tau_3 s_2 \left( \frac{\log p}{n} \right)^{3/2} + 3 C_2 s_1 s_2 \sqrt{\frac{\log p}{n}} + 3 C_2 C_\omega s_1 s_2 \frac{\log p}{n} \right) \\
= & \frac{1}{2} \left( \tau_1 \frac{1}{s_1s_2} + \tau_2 \frac{1}{s_1} + \tau_3 \frac{\log p}{s_1 n} + 3 C_2 + 3 C_2 C_\omega \sqrt{\frac{\log p}{n}} \right) s_1 s_2 \sqrt{\frac{\log p}{n}} \\
= & : b \cdot s_1 s_2 \sqrt{\frac{\log p}{n}}.
& \frac{\tau_4}{2} s_2 \left( \frac{\log p}{n_y} \right)^2 + \frac{2C_\omega}{\lambda_{\min}} \lambda_2 \sqrt{\frac{s_2 \log p}{n_y}} \\
= & \frac{\tau_4}{2} s_2 \left( \frac{\log p}{n_y} \right)^2 + \frac{2C_2 C_\omega}{\lambda_{\min}} \left( 1+C_\omega \sqrt{\frac{\log p}{n_y}} \right) s_1 s_2 \frac{\log p}{\sqrt{nn_y}} \\
